---
title: "HR Analytics"
output: html_notebook
---

```{r load libraries and helper functions}
source('helper.R')
source('libraries.R')
```

## Load the data.

```{r load the data}
mydata <- read_excel('data/HR Data.xlsx', na = "NA") %>%
  mutate(DOL = as.factor(if_else(DOL == "No", "0", 
                                 if_else(DOL == "Yes", "1", DOL)))) %>%
  select(-Functionality) %>%
  as.data.frame()

head(mydata)
```


Load the file containing the split functionality column (these columns are not used for this iteration but will be used subsequently).

```{r load functionality file}
functionality_df <- read.csv('data/functionality_split.csv', stringsAsFactors = FALSE)
```

Merge the mydata and functionality_df based on EmpCode.

```{r merge mydata and functionality}
mydata <- base::merge(mydata, functionality_df)
```

Split 70% of the data into the training set and 30% into the test set.

```{r split into train and test}
dat <- train_test_split(mydata, DepVar = 'DOL', Split = 0.7, seed = 1)
train <- dat$train
test <- dat$test

X_train <- select(train, -DOL)
Y_train <- select(train, DOL)

X_test <- select(test, -DOL)
Y_test <- select(test, DOL)

rm(mydata, dat, train_test_split, functionality_df)
```

## Pre-process Training Set

Remove the columns that are not used for this iteration and rename the Productivity% and Quality% columns.
```{r remove useless columns}
x_train <- X_train %>%
  select(-Empcode, -Name, -rec_id, -NT_UserName, -UserId, -ExitInitiatedOn, -Absconding, -PrevCompanyName, -L1Supervisor, -L2Supervisor, -Designation, -HighestDegree, -Major, -Client)  %>%
  rename(productivity = `Productivity%`, quality = `Quality%`)

y_train <- Y_train
```

Convert DOJ (Date of Joining) and DOB (Date of Birth) to dates and find the age at joining in days.

```{r age at joining}
x_train$DOJ <- ymd(x_train$DOJ)
x_train$DOB <- ymd(x_train$DOB)
x_train$age_at_joining <- as.numeric(difftime(time1 = x_train$DOJ, time2 = x_train$DOB))
```

Fill NA values in Per_Pincode by values in Pre_Pincode.

```{r fill NA Values in Per_Pincode}
x_train$Per_Pincode[is.na(x_train$Per_Pincode)] <- x_train$Pre_Pincode[is.na(x_train$Per_Pincode)]
```

Create a new variable whether Pre_Pincode and Per_Pincode are same.

```{r Pre_Pincode and Per_Pincode are the same}
x_train$Pre_Pincode <- as.character(x_train$Pre_Pincode)
x_train$Per_Pincode <- as.character(x_train$Per_Pincode)

x_train <- x_train %>%
  mutate(pin_code_diff = if_else(Pre_Pincode == Per_Pincode, 0, 1))
```

Remove the columns that are not needed now.

```{r remove columns not needed}
x_train <- x_train %>%
  select(-DOJ, -DOB, -Pre_Pincode, -Per_Pincode, -MLAvailed)
```

Convert values for PrevCompExp less than 0 to 0 and log transform it after adding 1.

```{r transfrom PrevCompExp}
x_train$PrevCompanyExp[x_train$PrevCompanyExp < 0] <- 0
x_train$PrevCompanyExp <- log(x_train$PrevCompanyExp + 1)
```

Create three new variables - whether both productivity and quality are NA, only productivity is NA or only quality is NA.

```{r NAs in Productivity and Quality}
x_train <- x_train %>%
  mutate(prod_qual_both = if_else(is.na(productivity) & is.na(quality) | 
                                    productivity == 0 & is.na(quality), 1, 0), 
         prod_only = if_else(is.na(productivity) & !is.na(quality), 1, 0), 
         qual_only = if_else(!is.na(productivity) & is.na(quality), 1, 0))
```

Replace NAs in productivity and quality by the median of the respective columns.

```{r NAs in productivity and quality by median}
median_productivity <- median(x_train$productivity, na.rm = TRUE)
median_quality <- median(x_train$quality, na.rm = TRUE)

x_train$productivity[is.na(x_train$productivity)] <- median_productivity
x_train$quality[is.na(x_train$quality)] <- median_quality
```

Remove the functionality column since as stated earlier this will be used in the next iteration.

```{r remove functionality}
x_train <- x_train %>%
  select(-main_func, -sub_func)
```

Create a new variable whether there are zero dependents.

```{r zero dependent variable}
x_train <- x_train %>%
  mutate(dep_zero = ifelse(Dependents == 0, 1, 0)) %>%
  select(-Dependents)
```

Take a look the final pre-processed train set.

```{r head(x_train)}
head(x_train)
```


## Pre-process Test Set

Following a similar procedure to the train set, preprocess the test set.

```{r preprocess test set}
x_test <- X_test %>%
  select(-Empcode, -Name, -rec_id, -NT_UserName, -UserId, -ExitInitiatedOn, -Absconding, -PrevCompanyName, -L1Supervisor, -L2Supervisor, -Designation, -HighestDegree, -Major, -Client)  %>%
  rename(productivity = `Productivity%`, quality = `Quality%`)

y_test <- Y_test

x_test$DOJ <- ymd(x_test$DOJ)
x_test$DOB <- ymd(x_test$DOB)
x_test$age_at_joining <- as.numeric(difftime(time1 = x_test$DOJ, time2 = x_test$DOB))

x_test$Per_Pincode[is.na(x_test$Per_Pincode)] <- x_test$Pre_Pincode[is.na(x_test$Per_Pincode)]

x_test$Pre_Pincode <- as.character(x_test$Pre_Pincode)
x_test$Per_Pincode <- as.character(x_test$Per_Pincode)
x_test <- x_test %>%
  mutate(pin_code_diff = if_else(Pre_Pincode == Per_Pincode, 0, 1))

x_test <- x_test %>%
  select(-DOJ, -DOB, -Pre_Pincode, -Per_Pincode, -MLAvailed)

x_test$PrevCompanyExp[x_test$PrevCompanyExp < 0] <- 0
x_test$PrevCompanyExp <- log(x_test$PrevCompanyExp + 1)

x_test <- x_test %>%
  mutate(prod_qual_both = if_else(is.na(productivity) & is.na(quality) | 
                                    productivity == 0 & is.na(quality), 1, 0), 
         prod_only = if_else(is.na(productivity) & !is.na(quality), 1, 0), 
         qual_only = if_else(!is.na(productivity) & is.na(quality), 1, 0))

x_test$productivity[is.na(x_test$productivity)] <- median_productivity
x_test$quality[is.na(x_test$quality)] <- median_quality

x_test <- x_test %>%
  select(-main_func, -sub_func)

x_test <- x_test %>%
  mutate(dep_zero = ifelse(Dependents == 0, 1, 0)) %>%
  select(-Dependents)
```

## Modeling

### Logistic Regression

```{r fit the model}
glm.model <- glm(formula = DOL ~ ., 
                 data = data.frame(x_train, y_train), 
                 family = binomial(link = 'logit'))

summary(glm.model)
```


```{r predict on test set}
# predict on the test set
pred_prob_test_glm <- predict(glm.model, newdata = x_test, type = 'response')
pred_vals_test_glm <- as.factor(ifelse(pred_prob_test_glm >= 0.5, 1, 0))
```

Confusion Matrix.

```{r confusion matrix}
caret::confusionMatrix(pred_vals_test_glm, y_test$DOL, mode = 'prec_recall', positive = '1')
```


```{r AUC}
roc(y_test$DOL, pred_prob_test_glm)$auc
```
